---
title: "Homework1"
author: "Christine Hou"
date: "2022-09-26"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Input Preparation

```{r}
library(tidyverse)
library(dbplyr)
library(nycflights13)
```


### 1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r,comment=NA}
sum(is.na(flights$dep_time))
```

There are 8255 flights are missing.

```{r,comment=NA}
flights %>% filter(is.na(dep_time))
```

The flights with missing `dep_time`, the variables including `dep_delay`,`arr_time`,`arr_delay`,`air_time` are also missing. This actually means that these flights are cancelled by airlines. 

### 2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
flights = mutate(flights,
                   dep_time_minutes = dep_time %/% 100 * 60 + dep_time %% 100,
                   sched_dep_time_minutes = sched_dep_time %/% 100 * 60 + sched_dep_time %% 100)
select(flights, starts_with('dep_time'), starts_with('sched'))
```

### 3. Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with `ggplot(aes(x= ,y=)) + geom_point()`

```{r}

```




